Highly Available Transactions: Virtues and Limitations

### 2013-04-01 writeup/hat-analysis.tex
cleaning
tweaks

We illustrate the hierarchy of available, sticky available, and
unavailable consistency models we have discussed in
Figure~\ref{fig:hatcompared}. Many models are simultaneously
achievable, but we find several particularly compelling. If we combine
all sticky-HAT guarantees, we have transactional, causal snapshot
reads. If we combine TA and P-CI, we have transactional snapshot
reads. We can achieve RC, MR, and RYW by simply sticking clients to
servers. And we can also combine unavailable models---for example, an
unavailable system might provide PRAM and One-Copy
Serializability~\cite{daudjee-session}.

@@

Composition cost also varies by combination. For instance, Charron-Bost
has proven that, to capture causality between $N$ communicating
processes, standard vector-based approaches face an upper bound of
$O(N)$ storage per write~\cite{charron-bost}. This means that, with
$100K$ clients, each write might be accompanied by $100K$ timestamps
per vector. This is difficult to scale. By compromising on
availability (e.g., treating a datacenter as a linearizable cluster),
this overhead can be reduced~\cite{cops, eiger}, but it is much
cheaper to provide, say, read your writes, than full causal
consistency.

>>>>

We illustrate the hierarchy of available, sticky available, and
unavailable consistency models we have discussed in
Figure~\ref{fig:hatcompared}. Many models are simultaneously
achievable, but we find several particularly compelling. If we combine
all sticky-HAT guarantees, we have transactional, causal snapshot
reads (i.e., Causal Transactional Predicate Cut Isolation). If we
combine TA and P-CI, we have transactional snapshot reads. We can
achieve RC, MR, and RYW by simply sticking clients to servers. And we
can also combine unavailable models---for example, an unavailable
system might provide PRAM and One-Copy
Serializability~\cite{daudjee-session}.

@@

Composition cost also varies by combination. For instance, Charron-Bost
has proven that, to capture causality between $N$ communicating
processes, standard vector-based approaches face an upper bound of
$O(N)$ storage per write~\cite{charron-bost}. This means that, with
$100K$ clients, each write might be accompanied by $100K$ timestamps
per vector. This is difficult to scale. By compromising on
availability (e.g., treating a datacenter as a linearizable cluster),
this overhead can be reduced~\cite{eiger}, but it is much
cheaper to provide, say, read your writes, than full causal
consistency.
